VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-07-17 snapshot_system/paper_eval.tex
re

\comments{
alg     efficiency
\scriptsize{}VC-2\%\tiny{}No\ Similarity        94.3132243792193
\scriptsize{}VC-NoPDS   93.0202119345744
\scriptsize{}VC-2\%PDS  96.0127647380588
\scriptsize{}VC-4\%PDS  96.5784837160482
\scriptsize{}SRB        97.8625610883421
}
\begin{table}[htb]
\centering
\begin{small}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
     no-simi&   &&  &    \\ \hline
     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
    \end{tabular}
\end{small}
    \caption{Deduplication efficiency for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}

>>>>

\comments{
alg     efficiency
\scriptsize{}VC-2\%\tiny{}No\ Similarity        94.3132243792193
\scriptsize{}VC-NoPDS   93.0202119345744
\scriptsize{}VC-2\%PDS  96.0127647380588
\scriptsize{}VC-4\%PDS  96.5784837160482
\scriptsize{}SRB        97.8625610883421
}
\begin{table}[htb]
\centering
\begin{small}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline 
&
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
&
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
&     no-simi&   &&  &    \\ \hline
Dedup &     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
Mem(MB) &     108&  46 & 118  & 190 & 2400 \\ \hline
    \end{tabular}
\end{small}
    \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}
